\label{sec:related-work}
A representative tool from the software visualization literature is
CodeSurveyor, by Hawes et al~\cite{hawes15:_codes}, which visualizes large
codebases using the analogy of cartographic maps. While it
incorporates dependency information into the layout of the map, VizAPI
differs from CodeSurveyor in that VizAPI focusses on usage relationships
between different modules (e.g. API invocations) using test
cases and static analysis to identify relationships between clients and libraries, rather
than investigating a particular system, as CodeSurveyor does.  Earlier
work includes the software cartography project by Kuhn et
al~\cite{kuhn10:_softw} and software terrain maps by DeLine~\cite{deline05:_stayin}.

% could mention
%software visualization/history animation:

%Gource
%code_swarm https://effectivesoftwaredesign.com/2012/05/24/code-swarm-visualizing-the-evolution-of-software-systems/

%% There is a large body of work investigating API usages, particularly
%% in mining API specifications, as first introduced by Ammons et
%% al~\cite{AmmonsETAL02MiningSpecifications}. 
%% Saied et
%% al~\cite{saied15:_minin_multi_api_usage_patter} studied which API
%% calls tended to co-occur in client code and inferred co-usage
%% relationships between these calls. Like them, we are specifically not
%% investigating sequencing relationships between API calls.

Hejderup and Gousios~\cite{DBLP:journals/jss/HejderupG22} explore a
question which is central to our approach---how well do client tests
exercise their dependencies' libraries? The dynamic part of our approach relies on
client test suites exercising enough of the dependencies to get valid
dynamic results from our analyses. They conclude that a combination of
static and dynamic analysis of the client has some chance of detecting
breaking changes in its dependencies, and we accordingly use static
analysis to supplement our dynamic results.

%% Thummalapenta and Xie~\cite{thummalapenta08:_spotw} presented
%% SpotWeb, which identifies framework hotspots (often-used APIs) and coldspots (never-used APIs).
%% Their notion of API
%% usage is similar to ours, but they perform a static search to identify
%% uses, while we additionally dynamically observe test executions. They
%% also identify the top $N$ percent of used APIs as hotspots, and unused
%% APIs as
%% coldspots. Viljamaa~\cite{viljamaa03:_rever_engin_framew_reuse_inter}
%% also identified hotspots, via concept analysis.

Call graph visualization is, of course, a well-known technique, as seen e.g. by the Reacher tool~\cite{latoza11:_visual_call_graph}. 
VizAPI also presents static and dynamic call information. However, we designed
it to support decisions about library/client interactions: the granularity of nodes is packages (typically it is methods);
and the layout is influenced by frequency of interactions.

Our overall goal is to help both client and library developers understand
client uses of library code. Clients benefit from sharpened warnings
about unsafe upgrades, knowledge that some upgrades are safe, and
having reduced attack surfaces. Library upgrades have been
investigated by many researchers, including Lam et
al~\cite{lam20:_puttin_seman_seman_version} and Kula et al~\cite{kula18:_do_devel_updat_their_librar_depen}. Kula et al found that most
software had outdated dependencies, and that software developers disliked being required to constantly upgrade their
libraries. Kula et al~\cite{kula14:_visual_evolut_system_their_librar_depen} also developed a tool
to visualize changes in dependencies over time---but not how a particular client depends on its libraries. 
Our VizAPI tool's dependency visualizations will help developers
prioritize required upgrades as low-effort or high-effort.
Foo et al~\cite{foo18:_effic_static_check_librar_updat}
proposed a static analysis which detected safe upgrades, but could
only certify safety for 10\% of upgrades; our combined static and
dynamic approach presents the developer with more information and
enables more upgrades. 

Bergel et al~\cite{bergel14:_domain_specif_languag_visual_softw_depen_graph} propose the {\sc Graph} DSL
for software visualizations. That language could generate static representations similar to VizAPI's; however,
VizAPI chooses a specific point in the design space, and we argue that this point is useful for helping developers understand
potential impacts of upgrades.
